Online resolving assembly graph by ONT long reads data

### 2019-05-28 paper.tex
draft 0.2

%Set abstract (see below)
\abstract{This is abstract}

>>>>

%Set abstract (see below)
\abstract{
A real-time assembly pipeline for Oxford Nanopore Technology (ONT) data is important for either better control of sequencing resources or quick turnaround of analyses. The previous approach from \npscarf{} provided a greedy fast-response, auto-correct streaming algorithm for such task but was relatively prone to mis-assemblies. Here we present another real-time hybrid assembler, \npgraph{}, that work on the assembly graph instead of the pre-assembled contigs. The results show improved accuracy while still minimize the required computational cost. The tool is available at \url{https://github.com/hsnguyen/assembly}.
}
